---
title: "Indeed Enterprise UXR Questions"
output: html_notebook
Author: Taylor Haaff
---

---
QUESTIONS
1. Determine if there are differences in NPS score by country.

  a. Are any differences statistically significant, and how did you decide?
  
2. Is there a difference in NPS by number of jobs posted?

  a. Are any differences statistically significant, and how did you decide?
  
3. Company leadership is interested in segmenting NPS data by company size, but we don’t collect the size of the company. 
What segmentation strategy would you suggest based on the data available?

  a. Why did you choose that segmentation strategy?
  
  b. What would you suspect are 1-2 dangers from this approach, and how would you
  convey these to company leadership? Why is your strategy still viable despite
  those dangers?
  
4. What strategies/methodologies would you use to extract the most common themes in
verbatim responses from customers in the NPS survey?

  a. What are some themes in these responses? If you’re able to execute some code
  to find some themes, great, but don’t spend too much time here. It’s more important to demonstrate your understanding of methodologies.

---
First import some things I'll probably need
```{r}
library(ggplot2)
library(tidyverse)
library(broom)
library(dplyr)
```


Read in all the data
n.b. nps = The Net Promoter Score, a 0-10 rating of how likely someone would be to recommend the product, higher is better
```{r}
country = read.csv('/Users/thaaff/Downloads/indeedquantitativeuxresearcher/country (1) (2).csv')
jobs = read.csv('/Users/thaaff/Downloads/indeedquantitativeuxresearcher/jobs (1) (2).csv')
nps = read.csv('/Users/thaaff/Downloads/indeedquantitativeuxresearcher/nps (1) (2).csv')
verbatims = read.csv('/Users/thaaff/Downloads/indeedquantitativeuxresearcher/verbatims (1) (2).csv')
```

---
1. Determine if there are differences in NPS score by country.
  a. Are any differences statistically significant, and how did you decide?

```{r}

#group by country code
by_country = country %>%
  group_by(billing_country_code) %>%
  summarise(nps = mean(nps_score),
            count = n())
#some of these countries have small amounts of data, the range is 1-12848
#we might want to look at only a subset

summary(by_country)
sd(by_country$nps)
```
The sd and IQR are pretty large compared to the range, lets see what it looks like if we look at the top 40 or 20 countries.

Top 40
```{r}
top40 = head(arrange(by_country,desc(count)), n = 40)
summary(top40)
sd(top40$nps)
```

Top 20
```{r}
top20 = head(arrange(by_country,desc(count)), n = 20)
summary(top20)
sd(top20$nps)
```

Nearly 95% (94.49%) of our data comes from the top 20 countries, and 99% (99.12%) comes from the top 40.
Even though multiple tests decreases statistical power I'll test all the data, then the top 40, then the top 20 to compare. 
I'll use a one-way ANOVA to check for a difference in mean nps between countries.

For the ANOVA to work we need all the individual entries, not the grouped data
```{r}
cut40 = filter(country, billing_country_code %in% top40$billing_country_code)
cut20 = filter(country, billing_country_code %in% top20$billing_country_code)
```


ANOVAs
```{r}
full_aov = aov(nps_score ~ billing_country_code, data = country)
top40_aov = aov(nps_score ~ billing_country_code, data = cut40)
top20_aov = aov(nps_score ~ billing_country_code, data = cut20)

summary(full_aov)
summary(top40_aov)
summary(top20_aov)
```

Large F-statistic and small p-values are both indicative of significance.
As it turns out, whether you look at the whole data set, the top 40 or the top 20 the difference between countries is always significant. 


---
2. Is there a difference in NPS by number of jobs posted?

  a. Are any differences statistically significant, and how did you decide?

Need a df with NPS and number of jobs, merge on advertiserID. 
```{r}
advertisers = merge(x = jobs, y = nps, by.x = 'metadataAdvertiserId', by.y = 'advertiser_id', all.x = TRUE)
```

nps is supposed to be a number from 0-10 but for some reason there are some entries larger than 10, only 3 advertisers have nps > 10 after the merge
```{r}
summary(advertisers)
hist(advertisers$nps_score)
#nps is not normally distributed, this shouldn't matter here because we have a fairly large data set, but it is worth noting.

plot(advertisers$nps_score ~ advertisers$distinct.jobid.)
#there are many more advertisers with few distinct jobs posted
```

Since dependent and independent variable are continuous we can't do an ANOVA again, I'll do a simple linear regression. 
```{r}
postnumber_nps_lm = lm(nps_score ~ distinct.jobid., data = advertisers)
summary(postnumber_nps_lm)
```
The F-statistic for this model is very small and the p-value is very large (p>>0.05, p = 0.9578), meaning there is no significant relationship between 
the number of jobs posted by an advertiser and their nps.















